FEM Model Analysis

### 2020-11-27 FEM_R/model_analysis.Rmd
More changes to transition models trying to improve on the T-tests

require(tidyverse)
require(formattable)
require(reactable)
require(haven)
require(data.table)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

>>>>

require(tidyverse)
#require(formattable)
require(reactable)
require(haven)
require(data.table)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

# Github Reporting

It would be nice if we could copy paste tables directly from this document into a github issue. For this reason, we will look into a package that can print tables directly into markdown or something similar, which we can then place straight into a Github issue.

```{r}

#kable
